%% thesis.tex 2014/04/11
%
% Based on sample files of unknown authorship.
%
% The Current Maintainer of this work is Paul Vojta.

\documentclass[masters]{ucbthesis}
\usepackage{biblatex}
\usepackage{graphicx}
\graphicspath{{./figs/}}
\usepackage{circuitikz}
\usepackage{subcaption}
% To compile this file, run "latex thesis", then "biber thesis"
% (or "bibtex thesis", if the output from latex asks for that instead),
% and then "latex thesis" (without the quotes in each case).

% Double spacing, if you want it.  Do not use for the final copy.
% \def\dsp{\def\baselinestretch{2.0}\large\normalsize}
% \dsp

% If the Grad. Division insists that the first paragraph of a section
% be indented (like the others), then include this line:
% \usepackage{indentfirst}

\newtheorem{theorem}{Jibberish}

\bibliography{references}

\hyphenation{mar-gin-al-ia}
\hyphenation{bra-va-do}

\begin{document}

% Declarations for Front Matter

\title{Closing the Analog Design Loop with BAG}
\author{Nicholas Werblun}
\degreesemester{Spring}
\degreeyear{2019}
\degree{Master of Science}
\chair{Professor Vladimir Stojanovi\'c}
\othermembers{Professor Borivoje Nikolic}
\numberofmembers{1}
\field{Electrical Engineering and Computer Sciences}
% Designated Emphasis -- this is optional, and rare
% \emphasis{Colloidal Telemetry}
% This is optional, and rare
% \jointinstitution{University of Western Maryland}
% This is optional
\campus{Berkeley}

% For a masters thesis, replace the above \documentclass line with
% \documentclass[masters]{ucbthesis}
% This affects the title and approval pages, which by default calls this
% document a "dissertation", not a "thesis".

\maketitle
% Delete (or comment out) the \approvalpage line for the final version.
% \approvalpage
\copyrightpage
\include{signature_sheet}
\include{abstract}

\begin{frontmatter}

%\begin{dedication}
%\null\vfil
%\begin{center}
%To my friends and family\\\vspace{12pt}
%Thank you for being there when I needed it. You know who you are.
%\end{center}
%\vfil\null
%\end{dedication}

% You can delete the \clearpage lines if you don't want these to start on
% separate pages.

\tableofcontents
\clearpage
\listoffigures
\clearpage

\begin{acknowledgements}
Thank you to professor Vladimir Stojanovi\'c for the advising and guidance through this project. Starting is often the hardest part, as is finding a direction to follow. Huge thank you to Sidney Buchbinder and Ruocheng Wang for mentoring me through my degree. Thank you for answering my multi-hundreds of questions and teaching me roughly one semester's worth of information in just a few weeks total.  I asked for design experience and I got it; and you helped me through it.

Additional thanks to Olivia for telling me to join the group. Thanks to Kourosh for helping by making the test bench circuits and helping with testing. Finally a thanks to all the rest of team Vlada: Panos, Christos, Pavan, Nandish, Taewhan and Eric for making my research experience go smoothly. Finally, thank you to Eric Chang et. al. for creating BAG so that I never had to do layout by hand.

\end{acknowledgements}

\end{frontmatter}
\pagestyle{headings}

% (Optional) \part{First Part}

\include{chap1}
\include{chap2}
\include{chap3}
\include{chap4}
\include{chap5}
% \appendix
% \chapter{More Monticello Candidates}

\printbibliography

\end{document}